\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}

\title{LatexIt}
\author{Auto-translator built by SHASHVAT SRIVASTAVA}
\date{November 2019}

\begin{document}2012\\
9/5\\
Lecture I
\begin{itemize}
\item  professor has a math PhD???
\item  other professor does chemistry ??? Wanted to study drama too
\end{itemize}
Important central idea of this class: unifying\\
principles.\\
Not facts\\
only!\\
Important stuff
\begin{itemize}
\item  Read the course website.
I - Course policies, recitation sections, etc.
\begin{itemize}
\item  Office hours, recitations start next week
\end{itemize}
\item  Fill out the mock submission survey!
\item  MITX?
\item 4 exams + final. (This is a change!) Also you can drop an exam.
You Do need to show up.
\item  Problem sets cannot be late. Collaboration is fine, but not copying.
\item  Different styles of learning
\begin{itemize}
\item  Paper textbook (Life), series of videos (see MITX), online textbook (!)
\item  Choose what you want for your own learning
\end{itemize}
\end{itemize}
What is this class?
\begin{itemize}
\item  Medicine rapidly developing in the present
\item  Cancer therapy, etc.
\item  DNA fingerprinting - then privacy issues, ancestry etc.
\item  Constantly changing \& driving forward? Things like genome editing!
"Diversity of life" - what's the common operating system?
Different "levels" - biospheres, ecosystems, organisms, organs, tissues, cells,
organelles, molecules (big to small)
We focus on the small things because they are common.
\item  Evolution - we won't talk much about it. 60 secondsi
– 4.5 billion years – Earth forms
0.5 billion yr - multicellular
4 billion yr - cools.
23.7 billion
0.005 billion yr - human-like
V 2200 21.5 billion - first nucleated cells I
lineage
renkamotes)
0.001 billion – Homo sapiens
0.0000002 billion – MIT founded.
\end{itemize}
organisms!\\
300\\
rms, somehow\\
(prokaryotes)\\
\end{document}