2012
\\9/5
\\Lecture I
\\-\begin{itemize}\item  professor has a math PhD???
-\item  other professor does chemistry ??? Wanted to study drama too
\end{itemize}
Important central idea of this class: unifying
\\principles.
\\Not facts
\\only!
\\Important stuff
\\•\begin{itemize}\item  Read the course website.
I -\item  Course policies, recitation sections, etc.
\end{itemize}
-\begin{itemize}\item  Office hours, recitations start next week
•\item  Fill out the mock submission survey!
1. MITX?
1.4 exams + final. (This is a change!) Also you can drop an exam.
\end{itemize}
You Do need to show up.
\\1. Problem sets cannot be late. Collaboration is fine, but not copying.
\\•\begin{itemize}\item  Different styles of learning
\end{itemize}
-\begin{itemize}\item  Paper textbook (Life), series of videos (see MITX), online textbook (!)
-\item  Choose what you want for your own learning
\end{itemize}
What is this class?
\\1. Medicine rapidly developing in the present
\\1. Cancer therapy, etc.
\\•\begin{itemize}\item  DNA fingerprinting -\item  then privacy issues, ancestry etc.
•\item  Constantly changing \& driving forward? Things like genome editing!
"Diversity of life" -\item  what's the common operating system?
Different "levels" -\item  biospheres, ecosystems, organisms, organs, tissues, cells,
\end{itemize}
organelles, molecules (big to small)
\\We focus on the small things because they are common.
\\•\begin{itemize}\item  Evolution -\item  we won't talk much about it. 60 secondsi
– 4.5 billion years – Earth forms
\end{itemize}
0.5 billion yr -\begin{itemize}\item  multicellular
4 billion yr -\item  cools.
23.7 billion
\end{itemize}
0.005 billion yr -\begin{itemize}\item  human-\item like
V 2200 21.5 billion -\item  first nucleated cells I
\end{itemize}
lineage
\\renkamotes)
\\0.001 billion – Homo sapiens
\\0.0000002 billion – MIT founded.
\\organisms!
\\300
\\rms, somehow
\\(prokaryotes)
\\