2012
9/5
Lecture I
-\begin{itemize}\item  p\end{itemize}rofessor has a math PhD???
-\begin{itemize}\item  o\end{itemize}ther professor does chemistry ??? Wanted to study drama too
Important central idea of this class: unifying
principles.
Not facts
only!
Important stuff
•\begin{itemize}\item  R\end{itemize}ead the course website.
I -\begin{itemize}\item  C\end{itemize}ourse policies, recitation sections, etc.
-\begin{itemize}\item  O\end{itemize}ffice hours, recitations start next week
•\begin{itemize}\item  F\end{itemize}ill out the mock submission survey!
1. MITX?
1.4 exams + final. (This is a change!) Also you can drop an exam.
You Do need to show up.
1. Problem sets cannot be late. Collaboration is fine, but not copying.
•\begin{itemize}\item  D\end{itemize}ifferent styles of learning
-\begin{itemize}\item  P\end{itemize}aper textbook (Life), series of videos (see MITX), online textbook (!)
-\begin{itemize}\item  C\end{itemize}hoose what you want for your own learning
What is this class?
1. Medicine rapidly developing in the present
1. Cancer therapy, etc.
•\begin{itemize}\item  D\end{itemize}NA fingerprinting -\begin{itemize}\item  t\end{itemize}hen privacy issues, ancestry etc.
•\begin{itemize}\item  C\end{itemize}onstantly changing \& driving forward? Things like genome editing!
"Diversity of life" -\begin{itemize}\item  w\end{itemize}hat's the common operating system?
Different "levels" -\begin{itemize}\item  b\end{itemize}iospheres, ecosystems, organisms, organs, tissues, cells,
organelles, molecules (big to small)
We focus on the small things because they are common.
•\begin{itemize}\item  E\end{itemize}volution -\begin{itemize}\item  w\end{itemize}e won't talk much about it. 60 secondsi
– 4.5 billion years – Earth forms
0.5 billion yr -\begin{itemize}\item  m\end{itemize}ulticellular
4 billion yr -\begin{itemize}\item  c\end{itemize}ools.
23.7 billion
0.005 billion yr -\begin{itemize}\item  h\end{itemize}uman-\begin{itemize}\item l\end{itemize}ike
V 2200 21.5 billion -\begin{itemize}\item  f\end{itemize}irst nucleated cells I
lineage
renkamotes)
0.001 billion – Homo sapiens
0.0000002 billion – MIT founded.
organisms!
300
rms, somehow
(prokaryotes)
